A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-09 0_reviewer_response.tex

\Que{
Moreover, the proposed technique seems to rely on rather accurate control of the width w of the deposited material, but it is not clear whether such control is achievable in practice. 
}
\Ans{
The photos of our print results already showed that adaptive width control is possible up to some (admittedly insufficient) extent.
We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: linear backpressure compensation.
We show the results of linear backpressure compensation in a separate figure which clearly shows the achieved variance in bead width.
}
\todo{
Show S5 prints. 
The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
}
\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b }
\paper{5.2 Printing results}{
\revise{}{
Test prints were performed on an unmodified Ultimaker S5 system,
with a standard  \SI{0.4}{\milli\meter} nozzle
and PLA filament
and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly.
However, that doesn't result in the intended filament outflow variation - see \cref{zero_backpressure}.
We conjecture that the filament outflow is related to the total pressure in the system,
which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
but also depends on the backpressure that the previous layer exerts on the filament protruding from the nozzle.
We conjecture that the amount of backpressure is monotonically related to the requested line width and compensate for the backpressure using a simple linear model:

\begin{align}
 v(w) &= \frac{f(w)}{h w} \\ 
% f &\sim p \\
% p &= p_\text{in} + p_\text{ext} \\
% p_\text{in} &= C \\
% p_\text{ext} &\sim w \\
% p_\text{ext} &= w / w^* - 1 \\
% f &= f^* - k p_\text{ext} \\
 f(w) &= f_0 - k \left( w / w_0 - 1 \right) \\
 f_0 &= v_0 w_0 h 
% v &= \frac{f^* - k p_\text{ext}}{h w} \\ 
% v &= \frac{v^* w^* h - k (w / w^* - 1)}{h w}
\end{align}
where
$v(w)$ is the movement speed as a function of requested bead width $w$,
$f(w)$ is the filament outflow,
$f_0$ is a constant reference flow
and
$k$ is the amount of backpressure compensation.
Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where
$v_0=\SI{30}{\milli\meter\per\second}$, 
$w_0=\SI{0.4}{\milli\meter}$.
See \cref{backpressure}.

\begin{figure}
\centering
\setlength{\figwidth}{0.32\columnwidth}
\setlength{\figheight}{0.5\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation-target.pdf}
\caption{Target widths}\label{backpressure_target}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[angle=90,height=\figheight]{sources-validation-zero-backpressure-compensation.png}
\caption{Constant filament inflow (\si{\milli\meter\cubed\per\second})}\label{zero_backpressure}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation.png}
\caption{Backpressure compensation}\label{backpressure}
\end{subfigure}
\caption{
Print results of varying width test on top of a dense white raft.
Trying to reproduce \subref{backpressure_target} without backpressure compensation ($k=0$) yields worse results \subref{zero_backpressure} than with backpressure compensation $k=1.1$ \subref{backpressure}.
}
\label{backpressure_compensation}
\end{figure}

}
}

@@

\Que{
At the same time, the scheme can potentially result in trajectories with many inflection points - this is slow and demanding for the machine. 
}
\Ans{
We have added statistics on fabrication time and discussed our findings.
See our response to 1.3.
}

\Que{
Finally, the examples provided depict the results obtained by the authors by "emulating" other techniques, but not with the actual results produced by the other techniques. While the reason behind this choice is easy to guess, it weakens the effectiveness of the claims. Adding careful discussions/extensions to support these questions would make the paper stronger.
}
\todo{
Discuss how much the over-fill / underfill and bead width variation depend on the fact that our reimplementations are only approximations.
}

\section{Reviewer 3}
Paper is well written. It is mostly easy to follow but overall, I find the the contributions somewhat incremental and the motivation not convincing. The paper mostly feels like a technical report. I am not sure if the methods overall teach enough to the researchers in the field to open up new research possibilities. My specific comments are below:

\Que{
The title is a little misleading that the presented approach may be used for general “Additive Manufacturing”. However, my understanding from the text is that it is designed particularly for FDM. I believe it is important to highlight this in the title. Otherwise, there should be enough evidence to prove that it can be applied to other kinds of printing processes, such as SLS, SLA, DMLS etc. 
}
The title has changed.
\revise{additive manufacturing}{fused deposition modeling}
\commits{64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0}
\paper{Title}{
A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}
}

@@

\Que{
It would be nice to discuss why contour-parallel toolpaths are needed or selected. In what situations, these are required as opposed to zigzag style (or direction-parallel as referred in the text) patterns. Without such a discussion, the motivation seems a little weak. In the second paragraph of introduction, there is a short discussion about this but it sounds like the authors assume that even the perimeters (or outline) are printed with direction-parallel extrusion. However, common approach in FDM is to print the perimeters with contour parallel toolpaths and fill the inner region with direction-parallel paths only (as later acknowledged in the related work 3rd paragraph). I think the motivation for contour parallel toolpaths needs to be justified further. 
}
\Ans{
The industry standard is to use a combination of contour-parallel and direction-parallel.
We now clarify why contour-parallel is (partly) used and that in as much as contour-parallel is used, our approach improves on the industry standard.
We have also developed and presented a new meta-scheme for generating only a limited number of perimeters, which shows that our technique is compatible with the industry standard for FDM 3D printing.
}

\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae ac800628951417dcb28bd6e3a0ed08801735acf4 a88ccd3309aef1233ed00ce9f22b244fe64668f4 077c8ee138bb311a8ba9abf303af4b09e973637a}
\paper{Intro}{
\revise{
Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
}{
Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
}
}
\paper{Abstract}{
\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
}

\Que{
Related work acknowledges the previous work sufficiently. However, the differences between the state of the art and the presented work are not clear. More discussion on where this work stands with respect to the state of the art is required. 
}
\Ans{
We have tried to address this in response to several other reviewers' comments.
See our response to 1.5, 1.1.1.
We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
}
\todo{link with other responses}
\commits{004894210fbc961f82b792fc702d1b67a1a8e8e8}
\paper{Fig 1}{
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}

\Que{
Isn’t it possible to put bounds on the width in the existing methods, such as the approach described in [9]? More discussion on that would be helpful. 
}
\Ans{
The bead width in Jin et al. is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.2$;
this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.2$.
We emphasized that our method (generally) results in a bead width deviation of $2$, rather than $3.2$ in the related work section and in the discussion section.
}
\commits{661d8f6766548c287cb174070432097e396d198f 92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d}
\paper{Intro}{
The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of \revise{$2$}{$3.2$}~\cite{Jin2017JMS},
}
\paper{Discussion}{
In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e. the deviation is within a factor of $3.2$.}
}
\paper{Discussion}{
\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads the bead widths range from $0.75w^*$ to $1.5w^*$, i.e. the deviation is within a factor $2$, which is considerably lower than in the centered scheme.}
We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width deviation} compared to the centered scheme.
}

@@

\Que{
What are the limitations of the presented algorithm? I do not see any discussions of the limitations of the algorithm.
}
\todo{
Linear approximations

a lot of direction changes (?)
}

\section{Other changes}
We have fixed some issues with positions and colors being swapped in the statistical analysis subfigures.
Fig 17f colors are adjusted.
Fig 17e and 17f are swapped.
\commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}

Improvements to abstract.
\commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
\paper{Abstract}{
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
}

@@

Fix double header of References.
\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}

Added patent notice and url to open source implementation.
\commits{ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a}
\paper{Intro}{
\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
}
